Compositionality and Modularity Together at Last!

### 2015-07-08 dAlg/mrm.tex
More text (up to Context)
Code for data type a la carte
Finishing up data type a la carte
Text for Grammars

\usepackage{xcolor}
\usepackage{xspace}
%\usepackage{amsmath}
%\usepackage{amsthm}
\usepackage{doubleequals}
\usepackage{comment}
\usepackage{url}
\usepackage{graphicx}
\usepackage[export]{adjustbox}
\graphicspath{ {images/} }

@@

%\input{sections/Extensibility}

@@

\input{sections/RecordAlg}

@@

>>>>

\usepackage{xcolor}
\usepackage{xspace}
%\usepackage{amsmath}
%\usepackage{amsthm}
\usepackage{doubleequals}
\usepackage{comment}
\usepackage{url}
\usepackage{graphicx}
\usepackage[export]{adjustbox}
\graphicspath{ {images/} }
\usepackage{dirtytalk}

@@

\input{sections/DTC}

@@

%\input{sections/RecordAlg}

\input{sections/Grammar}

@@

\bibitem{gibbons98}
  Gibbons, Jeremy and Jones, Geraint.
  The under-appreciated unfold.
  \emph{International Conference on Functional Programming},
  pages 273-279.
  Baltimore, Maryland, September 1998

\bibitem{swierstra08}
  Swierstra, Wouter.
  Datatypes \`a la Carte.
  \emph{Journal of Functional Programming},
  18(4):423-436,
  2008

\bibitem{oliveira12}
  Olivera, B.C.d.S, and Cook, William R.
  Functional Programming with Structured Graphs.
  \emph{ICFP '12 Proceedings of the 17th ACM SIGPLAN international conference on Functional programming},
  Pages 77-88,
  2012

\bibitem{chlipala08}
  Chlipala, A.
  Parametric higher-order abstract syntax for mechanized semantics.
  \emph{ICFP’08}, 
  2008.
